A Kochen-Specker system has at least 21 vertices\\ {\small (extended abstract)}

### 2014-04-14 main.tex
work

>>>>

Different assignments give different sentences.  In our tests,
some assignments would yield sentences that were decided within milliseconds,
whereas another assignment with less free vertices would
yield a sentence that could not be decided (directly).
Therefore, when determining embeddability of a graph,
we try several assignments in parallel.

In this way, there were still a few graphs that we could not decide.
By hand, we determined these graphs to be embeddable.
We addapted the algorithm, to in parallel for some assignments
to guess the position of one of the vectors.  If the corresponding
sentence turns out false, we know nothing.  However,
if the sentence is true, we know the graph is embeddable.

With this method, we have decided the embeddability of every squarefree
graph with minimal vertex order three of 13 vertices of less.
In particular:
\begin{comp}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal 20
    contains as a subgraph one of
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    which are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a direct proof.
